### 2018-01-27 README.Rmd
using binder

The goal of modelextinctionideas is to ...

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Title of compendium_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

@@

**Text and figures:**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code:** See the [DESCRIPTION](DESCRIPTION) file

$\textbf{Data:}$ [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

>>>>

[![Binder](http://mybinder.org/badge.svg)](http://mybinder.org/v2/gh/benmarwick/modelextinctionideas/master)

Ben Marwick, University of Washington    
Erik Gjesfjeld, University of Cambridge

The goal of modelextinctionideas is to make available the code and data for our SAA2018 poster presentation "Modelling the innovation and extinction of archaeological ideas"

@@

> Marwick, B and E. Gjesfjeld, (`r format(Sys.Date(), "%Y")`). _Research Compendium for 'Modelling the innovation and extinction of archaeological ideas'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

### Run the code in your broswer with Binder

Click on the pink binder button at the top, once inside Jupyter Notebook, RStudio Server should be an option under the menu "New" in the top right. Click on "New" in the top right, and at the bottom will be `RStudio Session`. Click that and your RStudio session will begin momentarily.

Download the files to your desktop, open `modelextinctionideas.Rproj` in RStudio, install the `modelextinctionideas` package (CTRL+SHIFT+B) then open `analysis/paper/paper.Rmd` and knit the Rmd to run the code and generate the results and plots found in the paper.

@@

**Text and figures: **  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code: ** See the [DESCRIPTION](DESCRIPTION) file

$\textbf{Data :}$ [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
